Establishing Trusted I/O Paths for Client \\ Shielded Execution Systems with Aurora

### 2019-07-04 article.tex
body review

% Author(s) Name
\author{Hongliang~Liang,~\IEEEmembership{Member,~IEEE,}
	Mingyu Li,%~\IEEEmembership{Fellow,~OSA,}
	~Lin Jiang,~Zhuosi Xie,~Tianqi Yang,~Yixiu Chen\\
	Trusted Software and Intelligent System Lab\\
	Beijing University of Posts and Telecommunications
  %, Tianqi Yang, Mingyue Li, Yudong Wang % <-this % stops a space
	\thanks{H. Liang, M. Li, L. Jiang, Z. Xie, T. Yang, Y. Chen 
  %, T. Yang, M. Li, and Y. Wang 
  are with Beijing University of Posts and Telecommunications, Beijing 100876, China. e-mail: (\{hliang,maxul,jianglin,xiezhuosi,yangtianqi,chenyixiu\}@bupt.edu.cn)
  %; yangtianqi@bupt.edu.cn; li\_mingyue@bupt.edu.cn; wyd2013@bupt.edu.cn
  }% <-this % stops a space
	\thanks{This work was supported by the National Natural Science Foundation of China (NSFC) under Grant No. U1713212 and 91418206.}
}

>>>>

% Author(s) Name
\author{Hongliang~Liang,~\IEEEmembership{Member,~IEEE,}
	Mingyu Li,~Yixiu Chen,~Lin Jiang,~Zhuosi Xie,~Tianqi Yang\\
	Trusted Software and Intelligent System Lab\\
	Beijing University of Posts and Telecommunications
	\thanks{H. Liang, M. Li, Y. Chen, L. Jiang, Z. Xie, T. Yang
  are with Beijing University of Posts and Telecommunications, Beijing 100876, China. e-mail: (\{hliang,maxul,jianglin,xiezhuosi,yangtianqi,chenyixiu\}@bupt.edu.cn)
  }% <-this % stops a space
}
